% issues.tex - Problem statement for new design
As a new design concept, SimpleChef addresses several recurring usability and workflow issues observed in existing cooking and meal-planning applications:

\begin{itemize}
  \item \textbf{Fragmented User Experience}: Users must often switch between multiple applications for recipes, meal planning, calorie tracking, and grocery lists. Context switching increases cognitive load and reduces the likelihood that users will maintain consistent meal planning or calorie tracking habits.
  \item \textbf{Poor Recipe Instruction Presentation}: Many recipe apps display instructions as long, uninterrupted paragraphs. During active cooking, users need scannable, step-by-step guidance with ingredients clearly associated with each step. Without ``mise en place'' (ingredients per step) visibility, users may miss ingredients or lose their place.
  \item \textbf{Ineffective Timer Integration}: Cooking often requires multiple timers (e.g., for pasta, sauce, and resting). Existing apps rarely integrate timers directly into recipe steps, forcing users to leave the app, use separate devices, or manually set external timers. This breaks flow and increases the risk of errors.
  \item \textbf{Manual Grocery List Management}: Building a grocery list from planned meals is tedious when done manually. Users must read through multiple recipes, aggregate ingredients, and deduplicate. Errors and omissions are common, especially when scaling recipes or adjusting servings.
  \item \textbf{Recipe Input Friction}: Adding recipes from text, images, or video sources typically requires manual retyping. Users who find recipes online or in cookbooks face high barriers to importing them into a structured format, which discourages adoption of digital recipe management.
  \item \textbf{Inflexible Calorie and Diet Tracking}: Calorie tracking in generic apps does not integrate with recipes or meal plans. Users cannot easily see how planned meals contribute to daily goals or filter recipes by dietary restrictions without manual cross-referencing.
\end{itemize}

These problems form the problem statement that SimpleChef aims to solve through an integrated, user-centered design.
