% goals.tex
The primary goals of this project are to:

\begin{itemize}
  \item \textbf{Unify the Cooking Workflow}: Integrate recipe browsing, step-by-step cooking mode, meal planning, calorie tracking, and grocery list generation into a single, coherent application with consistent navigation and data flow.
  \item \textbf{Optimize the Step-by-Step Cooking Experience}: Design a cooking mode that displays only the relevant step, its associated ingredients (mise en place), and embedded timer triggers. The interface must remain legible and calm during active cooking, with minimal cognitive load.
  \item \textbf{Implement Intelligent Timer Management}: Provide a timer dock that displays active timers (stacked by least time remaining), expands on tap for full control, and integrates seamlessly into recipe steps so users never leave the cooking context.
  \item \textbf{Automate Grocery List Generation}: Auto-populate grocery lists from planned meals, deduplicate and categorize items, and allow full user control to edit, reorder, and export lists to notes or external apps.
  \item \textbf{Reduce Recipe Input Friction}: Support multiple input methods---paste text/URL, upload image, upload video, or manual entry---with AI-assisted parsing to structure ingredients and steps. Provide a verification and edit flow so users can correct parsing errors before saving.
  \item \textbf{Support Meal Planning and Calorie Goals}: Enable users to assign recipes to calendar days, view daily calorie totals against profile goals, and filter recipes by dietary restrictions. Provide optional statistics for trends over time.
  \item \textbf{Apply HCI Principles}: Design for clarity over clutter, progressive disclosure, and visual warmth. Validate the design through user testing and iteration to ensure usability, responsiveness, and aesthetic appeal.
\end{itemize}
